### 2016-05-25 paper/paper.tex
discussion section and defenses update

DDoSCoin adjusts difficulty for a given domain by looking at the past
BLOCK\_ADJUST blocks, and counting the number of blocks mined against
the given domain. This ratio is compared to the expected ratio based on the
current size of the victim list. If more blocks were mined than expected, the
difficulty for this domain is increased. Similarly, if fewer blocks were mined,
the difficulty for the domain is decreased.
This mechanism allows target domains that somehow become more
difficult to reach to quickly return to a more appropriate difficulty, without
having to wait for many blocks mined at the high difficulty.

At the same time, there is a global difficulty adjustment factor applied to all
domain difficulties that is computed based only on the number of blocks mined
over a given time. If blocks are being produced faster than expected, then the
difficulty on all blocks increases. Likewise, blocks coming in slower than
expected will reduce the global difficulty.

@@

A target's initial difficulty in DDoSCoin is decided by the stakeholder that
introduces the target in a proof-of-stake block. The stakeholder is incentivized to not
set the difficulty too low, as the DDoS would be ineffective. Also, many coins would be
mined quickly, devaluing the stakeholder's own coins. If the difficulty is set too high,
there will be a delay as other domains are mined, and the difficulty adjusts down
to the appropriate level. These are similar to the incentives for PAY\_TO\_DDOS 
transactions, mentioned in Section~\ref{sec:pay-to-ddos}.

@@

To evaluate the performance and effectiveness of DDoSCoin, we implement our
proof-of-DDoS function in 582 lines of C\@. Our mining code uses
libevent~\cite{libevent} and OpenSSL~\cite{openssl} to create concurrent
connections toward a specific target, testing each response to see if it
satisfies a hard-coded proof-of-DDoS target difficulty.

We tested our proof-of-DDoS function (miner) against a quad-core server under
our control, running nginx serving the default page and connected to our
attacker over a local Gigibit Ethernet network. When running our miner, the CPU
consumption of the server quickly reaches 100\% utilization on all 4 cores,
while the attacker only requires approximately 30\% on a single core. This
produces over 3000 TLS connections per second, and slows response times of the
webserver considerably. We used Apache benchmark (ab) with 1000 connections with
a concurrency of 50 to quantify this, and tested the server under normal
conditions (no miner running) and under DoS (miner running). As shown in
Figure~\ref{fig:eval}, we find that the average response time increases by more
than a factor of 6.

@@

Many positive results have come from cryptocurrencies.
Bitcoin was invented with the goal of creating a decentralized digital currency, 
and to that end has been more sucessful than most imagined. Banks are turning
to ``Blockchain technology'' to solve issues regarding public ledgers.
Primecoin and TorPath use cryptocurrencies to incentivize positive actions.
However, this positivity is not inherent to cryptocurrencies. DDoSCoin demonstrates
maliciousness inherent to a currency's design, turning the notion of what constitutes
a ``useful'' proof-of-work around. Certainly a DDoS attack it useful to someone,
but negatively impacts society as a whole.

DDoSCoin uses proof that the miner connected to a given server a sufficient number 
of times as its proof-of-work. This is an indirect measurement of how much bandwidth
to a given endpoint is being wasted by the miner. This provides a unique challenge
to the currency 
when miners have different bandwidths to that given endpoint. The extreme of 
having a different bandwidth is being the target, and having the private key 
for the site. Having this privileged position allows 
the target to actively engage in DDoSCoin as a defense. We discuss this further in
Section~\ref{sec:defense}.

@@

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
While we acknowledge this work introduces an idea that could be used to incentivize 
malicious behavior, the ethics of this paper are controlled. We only demonstrate a 
proof of concept, and in doing so, only attack websites we have ownership of.
Further, we do not publish the full coin.
We believe it important to fully disclose potential attacks, even those that
require the development of an altcoin to execute. This is especially important in the
face of the impending commitment to the design of TLS 1.3, and compounded by how long 
TLS/SSL protocol versions stay in active use. Further, proof-of-DDoS has applications 
beyond just DDoSCoin.

@@

>>>>

DDoSCoin adjusts difficulty for a given domain by looking at the previous
BLOCK\_ADJUST blocks, and counting the number of blocks mined against
the given domain. This ratio is compared to the expected ratio based on the
current size of the victim list and the time over which these blocks were mined
(based on a timestamp included in the blocks). If more blocks were mined than
expected, the
difficulty for this domain is increased. Similarly, if fewer blocks were mined,
the difficulty for the domain is decreased.
This mechanism allows target domains that somehow become more
difficult to reach to quickly return to a more appropriate difficulty, without
having to wait for many blocks mined at the high difficulty.

@@

A target's initial difficulty in DDoSCoin is decided by the stakeholder that
introduces the target in a proof-of-stake block. The stakeholder is incentivized to not
set the difficulty too low, as many coins would be
mined quickly, devaluing the stakeholder's own coins. If the difficulty is set too high,
there will be a delay as other domains are mined, and the difficulty adjusts down
to the appropriate level.
%These are similar to the incentives for PAY\_TO\_DDOS 
%transactions, mentioned in Section~\ref{sec:pay-to-ddos}.

@@

To evaluate the performance and effectiveness of DDoSCoin, we implement our
proof-of-DDoS function in 582 lines of C\@. Our mining code uses
libevent~\cite{libevent} and OpenSSL~\cite{openssl} to create concurrent
connections toward a specific target, crafting a
\texttt{client\_random} in the specified way and testing each response to see if it
satisfies a hard-coded proof-of-DDoS target difficulty.

We tested our proof-of-DDoS function (miner) against a quad-core TLS server under
our control, running nginx serving the default page and connected to our
attacker over a local Gigibit Ethernet network. When running our miner, the CPU
consumption of the server quickly reaches 100\% utilization on all 4 cores,
while the attacker only requires approximately 30\% on a single core. This
produces over 3000 TLS connections per second, and slows response times of the
webserver considerably. We used Apache benchmark (ab) with 1000 connections with
a concurrency of 50 to quantify this, and tested the server under normal
conditions (no miner running) and under DoS (miner running). As shown in
Figure~\ref{fig:eval}, we find that the average server response time increases by more
than a factor of 6 when our miner is running.

@@

Many positive results have come from cryptocurrencies.
Bitcoin was invented with the goal of creating a decentralized digital currency,
and to that end has been more sucessful than most imagined. Banks are turning
to ``Blockchain technology'' to solve issues regarding public ledgers.
Primecoin and TorPath use cryptocurrencies to incentivize positive actions.
However, this positivity is not inherent to cryptocurrencies. DDoSCoin demonstrates
maliciousness inherent to a currency's design, turning the notion of what constitutes
a ``useful'' proof-of-work around.

DDoSCoin uses a proof that the miner has connected to a given server a sufficient number 
of times as its proof-of-work. This is an indirect measurement of how much
bandwidth or resources are being spent by the victim. Although miners only
receive DDoSCoins in return for this effort, these can be traded in for other
currency via cryptocurrency exchanges. In addition, because DDoSCoin uses
transactions similar to Bitcoin, trust-less cross-chain transactions can allow
DDoSCoins to be traded for Bitcoins without requiring a trusted 3rd party
intermediary. Thus, even outlawing DDoSCoins from exchanges does not prevent a
black-market from getting around these sanctions.

@@

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
While we acknowledge this work introduces an idea that could be used to incentivize 
malicious behavior, we have taken precautions to limit harm. First, in
demonstrating our proof-of-concept and evaluating our proof-of-DDoS code, we
have only ``attacked'' websites we have ownership and authority over.
Further, we are not publishing a working alt-coin that uses this proof-of-DDoS,
but rather a conceptual description of one.
We believe it important to fully disclose potential attacks, even those that
require the development of an altcoin to execute. This is especially important in the
face of the impending commitment to the design of TLS 1.3, and compounded by how long
TLS/SSL protocol versions stay in active use.

%Further, proof-of-DDoS has applications 
%beyond just DDoSCoin.

@@

Although dramatically changing existing deployed versions of TLS is unrealistic, it may still
be possible to influence the design of the TLS 1.3 standard to make it
incompatible with DDoSCoin. For example, rather than having the server sign all
of the handshake messages (including those from the client), the server could
sign only the handshake messages which it sent. This may not fully mitigate
DDoSCoin, as some of the parameters (such as the selected cipher suite or
elliptic curves) may have originally been provided by the client. We note that
while the server signing only its own messages still mitigates many previous
known bugs such as those revealed in the FREAK TLS attack, there may be other subtle bugs that are
exposed by servers not signing client's messages.
